---
title: "FARS Coursera"
author: "Michael Rahija"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

# Purpose
The farscoursera package provides functions for analyzing data taken from the  Fatality Analysis Reporting (FARS) System which provides the yearly traffic accident fatatlities covering the entire United States. 

## make_filename
This function will build the file name for a year, as shown:

```{r }
library(farsCoursera)
library(dplyr)

file <- make_filename("2013")
file
```

## fars_read
This function reads in a dataset caontaining the FARS data for a particular year.
```{r }
df <- fars_read(file)
head(df)
```


## fars_read_years
This functions takes multiple years, and returns a list of data frames containing the FARS data for those years.
```{r }
df <- fars_read_years(c(2013,2014))
head(df)
```


## fars_summarize_years
This function takes a vector of strings (years) and returns a tibble containing the number of fatal injuries by year and month.If the years are not 2013-2015, there will be an error.
```{r }
df <- fars_summarize_years(c(2013,2014))
head(df)
```

## fars_map_state
This functions takes a state number and year, and returns a plot showing all traffic fatalities. If the years are not 2013-2015, or the number doesn't correspond to a state, there will be an error.
```{r }
plot <- fars_map_state(state.num = 4, year = 2013)
plot
```

